Tables for poster
=========

Load the Data
-----
First we load the data:

```{r}
library(ProjectTemplate)
library(Hmisc)
library(survey)
library(binom)
library(ggplot2)
library(scales)

setwd("~/Dropbox/Mike/CHIS")
load.project()
```

This also runs the script to clean the data, contained within the file `/munge/01-A.R`. The design object with 0-5 year olds is created by subsetting the design object from the full dataset. The subset design object is called `rchis05`.

Table 1: Univariates
-------
We want:  
* gender (male)
* birthweight  (brthwk.p.i)
* ethnicity  (srh.a.i)
* race  (racehp2p)
* below poverty level (belowpovl)
* PEDS risk categories (peds)
* age (srage.p)
* uninsured in the last year (unins.ever)
* Developmental specialist referred (cf46)
* speech referred (cf47)
* Referred to either (referred)

### Gender
```{r}
summary(chis$male)
length(chis$male)
binom.confint(sum(chis$male == "Male", na.rm = T), length(!is.na(chis$male)), method = "asym")

svytotal(~male, rchis05)
sum(svytotal(~male, rchis05))
svymean(~male, rchis05)
confint(svymean(~male, rchis05))

cbind(svymean(~male, rchis05), confint(svymean(~male, rchis05)))
```

### Age
```{r}
mean(chis$srage.p)
sd(chis$srage.p)
n.age <- length(chis$srage.p)
mean(chis$srage.p) + qt(0.025, n.age)
mean(chis$srage.p) + qt(0.975, n.age)

cbind(svymean(~srage.p, rchis05), confint(svymean(~srage.p, rchis05)))
```

### Birthweight
```{r}
summary(chis$brthwk.p.i)
mean(chis$brthwk.p.i)
sd(chis$brthwk.p.i)
n.bw <- length(chis$brthwk.p.i)
n.bw
mean(chis$brthwk.p.i) + qt(0.025, n.bw)
mean(chis$brthwk.p.i) + qt(0.975, n.bw)

cbind(svymean(~brthwk.p.i, rchis05), confint(svymean(~brthwk.p.i, rchis05)))
svyquantile(~brthwk.p.i, design = rchis05, quantiles = 0.5)
```

### PEDS
```{r}
summary(chis$peds)
pedstable <- table(chis$peds)
pedstable
sum(pedstable)
sapply(pedstable, binom.confint, n = sum(pedstable), method = "asy")

svytotal(~peds, rchis05, na.rm = T)
sum(svytotal(~peds, rchis05, na.rm = T))

cbind(svymean(~peds, rchis05, na.rm = T), confint(svymean(~peds, rchis05, na.rm = T)))
```

### Hispanic Ethnicity
```{r}
summary(chis$srh.a.i)
binom.confint(sum(chis$srh.a.i == "YES"), length(chis$srh.a.i), method = "asym")

svytotal(~srh.a.i, rchis05)
sum(svytotal(~srh.a.i, rchis05))

cbind(svymean(~srh.a.i, rchis05), confint(svymean(~srh.a.i, rchis05)))

```

### Race
```{r}
summary(chis$racehp2p)
racetable <- table(chis$racehp2p)
racetable
sapply(racetable, binom.confint, n = sum(racetable), method = "asy")

svytotal(~racehp2p, rchis05)
sum(svytotal(~racehp2p, rchis05))

cbind(svymean(~racehp2p, rchis05), confint(svymean(~racehp2p, rchis05)))
```

### Lack of Insurance
```{r}
ins.table <- table(chis$unins.ever)
ins.table
binom.confint(ins.table[2], sum(ins.table), method = "asym")

svytotal(~unins.ever, rchis05, na.rm = T)
sum(svytotal(~unins.ever, rchis05, na.rm = T))

cbind(svymean(~unins.ever, rchis05), confint(svymean(~unins.ever, rchis05)))
```

### Below Poverty Level
```{r}
summary(chis$belowpovl)
length(chis$belowpovl)
binom.confint(sum(chis$belowpovl == "Below 100% FPL", na.rm = T), length(!is.na(chis$belowpovl)), method = "asym")

svytotal(~belowpovl, rchis05, na.rm = T)
sum(svytotal(~belowpovl, rchis05, na.rm = T))

cbind(svymean(~belowpovl, rchis05), confint(svymean(~belowpovl, rchis05)))
```


### Referred to Developmental Specialist
```{r}
summary(chis$cf46)
length(chis$cf46)
table(chis$cf46)
sum(table(chis$cf46))
binom.confint(sum(chis$cf46 == "Referred", na.rm = T), sum(table(chis$cf46)), method = "asym")

svytotal(~cf46, rchis05, na.rm = T)
sum(svytotal(~cf46, rchis05, na.rm = T))

cbind(svymean(~cf46, rchis05, na.rm = T), confint(svymean(~cf46, rchis05, na.rm = T)))
```

### Referred to Speech, Language, Hearing Evaluation
```{r}
summary(chis$cf47)
length(chis$cf47)
table(chis$cf47)
sum(table(chis$cf47))
binom.confint(sum(chis$cf47 == "Referred", na.rm = T), sum(table(chis$cf47)), method = "asym")

svytotal(~cf47, rchis05, na.rm = T)
sum(svytotal(~cf47, rchis05, na.rm = T))

cbind(svymean(~cf47, rchis05, na.rm = T), confint(svymean(~cf47, rchis05, na.rm = T)))
```

### Referred to either Developmental Specialist or Speech, Language, Hearing Evaluation
```{r}
summary(chis$referred)
length(chis$referred)
table(chis$referred)
sum(table(chis$referred))
binom.confint(sum(chis$referred == "Yes", na.rm = T), sum(table(chis$referred)), method = "asym")

svytotal(~referred, rchis05, na.rm = T)
sum(svytotal(~referred, rchis05, na.rm = T))

cbind(svymean(~referred, rchis05, na.rm = T), confint(svymean(~referred, rchis05, na.rm = T)))
```

Table 2: Unadjusted Bivariate Comparisons
------
We will want to see what is the rate of referrals among children in each of those categories and whether they are significant. We must use the survey functions for weighting to test the associations.

### Gender
```{r}
svyby(~male, by = ~cf46, design = rchis05, FUN = svymean)
svychisq(~male + cf46, rchis05, statistic = "Chisq")

svyby(~male, by = ~cf47, design = rchis05, FUN = svymean)
svychisq(~male + cf47, rchis05, statistic = "Chisq")

svyby(~male, by = ~referred, design = rchis05, FUN = svymean)
svychisq(~male + referred, rchis05, statistic = "Chisq")
```

### Age
```{r}
svyby(~srage.p, by = ~cf46, design = rchis05, FUN = svymean)
svyttest(srage.p ~ cf46, design = rchis05)

svyby(~srage.p, by = ~cf47, design = rchis05, FUN = svymean)
svyttest(srage.p ~ cf47, design = rchis05)

svyby(~srage.p, by = ~referred, design = rchis05, FUN = svymean)
svyttest(srage.p ~ referred, design = rchis05)
```

### Birthweight
```{r}
svyby(~brthwk.p, by = ~cf46, design = rchis05, FUN = svymean, na.rm = T)
svyttest(brthwk.p ~ cf46, design = rchis05)

svyby(~brthwk.p, by = ~cf47, design = rchis05, FUN = svymean, na.rm = T)
svyttest(brthwk.p ~ cf47, design = rchis05)

svyby(~brthwk.p, by = ~referred, design = rchis05, FUN = svymean, na.rm = T)
svyttest(brthwk.p ~ referred, design = rchis05)
```

### Race
```{r}
svyby(~racehp2p, by = ~cf46, design = rchis05, FUN = svymean)
svychisq(~racehp2p + cf46, rchis05, statistic = "Chisq")

svyby(~racehp2p, by = ~cf47, design = rchis05, FUN = svymean)
svychisq(~racehp2p + cf47, rchis05, statistic = "Chisq")

svyby(~racehp2p, by = ~referred, design = rchis05, FUN = svymean)
svychisq(~racehp2p + referred, rchis05, statistic = "Chisq")
```

### Hispanic Ethnicity
```{r}
svyby(~srh.a.i, by = ~cf46, design = rchis05, FUN = svymean)
svychisq(~srh.a.i + cf46, rchis05, statistic = "Chisq")

svyby(~srh.a.i, by = ~cf47, design = rchis05, FUN = svymean)
svychisq(~srh.a.i + cf47, rchis05, statistic = "Chisq")

svyby(~srh.a.i, by = ~referred, design = rchis05, FUN = svymean)
svychisq(~srh.a.i + referred, rchis05, statistic = "Chisq")
```

### Below Poverty Level
```{r}
svyby(~belowpovl, by = ~cf46, design = rchis05, FUN = svymean)
svychisq(~belowpovl + cf46, rchis05, statistic = "Chisq")

svyby(~belowpovl, by = ~cf47, design = rchis05, FUN = svymean)
svychisq(~belowpovl + cf47, rchis05, statistic = "Chisq")

svyby(~belowpovl, by = ~referred, design = rchis05, FUN = svymean)
svychisq(~belowpovl + referred, rchis05, statistic = "Chisq")
```

### Uninsured Ever in Last Year
```{r}
svyby(~unins.ever, by = ~cf46, design = rchis05, FUN = svymean)
svychisq(~unins.ever + cf46, rchis05, statistic = "Chisq")

svyby(~unins.ever, by = ~cf47, design = rchis05, FUN = svymean)
svychisq(~unins.ever + cf47, rchis05, statistic = "Chisq")

svyby(~unins.ever, by = ~referred, design = rchis05, FUN = svymean)
svychisq(~unins.ever + referred, rchis05, statistic = "Chisq")
```

### PEDS High Risk
```{r}
svyby(~pedsHiRisk, by = ~cf46, design = rchis05, FUN = svymean)
svychisq(~pedsHiRisk + cf46, rchis05, statistic = "Chisq")

svyby(~pedsHiRisk, by = ~cf47, design = rchis05, FUN = svymean)
svychisq(~pedsHiRisk + cf47, rchis05, statistic = "Chisq")

svyby(~pedsHiRisk, by = ~referred, design = rchis05, FUN = svymean)
svychisq(~pedsHiRisk + referred, rchis05, statistic = "Chisq")
```

Table 2: Alternate Method by Odds Ratios
-----
We can also calculate the unadjusted odds ratios as below. We should probably write a function to automate this task but maybe this is too much effort.

### Gender
```{r}
model1 <- svyglm(cf46 ~ male, design = rchis05, family = quasibinomial)
model2 <- svyglm(cf47 ~ male, design = rchis05, family = quasibinomial)
model3 <- svyglm(referred ~ male, design = rchis05, family = quasibinomial)
stargazer(model1, model2, model3, type = "text",
          dep.var.labels = c("DS Only", "SLH Only", "Either DS or SLH"))

summary(model1)
summary(model2)
summary(model3)


cbind(OddsRatio = exp(model1$coef), exp(confint(model1)))
cbind(OddsRatio = exp(model2$coef), exp(confint(model2)))
cbind(OddsRatio = exp(model3$coef), exp(confint(model3)))
```

### Age
```{r}
model1 <- svyglm(cf46 ~ srage.p, design = rchis05, family = quasibinomial)
model2 <- svyglm(cf47 ~ srage.p, design = rchis05, family = quasibinomial)
model3 <- svyglm(referred ~ srage.p, design = rchis05, family = quasibinomial)

summary(model1)
summary(model2)
summary(model3)

cbind(OddsRatio = exp(model1$coef), exp(confint(model1)))
cbind(OddsRatio = exp(model2$coef), exp(confint(model2)))
cbind(OddsRatio = exp(model3$coef), exp(confint(model3)))

stargazer(model1, model2, model3, type = "text")
```

### Birthweight
```{r}
model1 <- svyglm(cf46 ~ brthwk.p.i, design = rchis05, family = quasibinomial)
model2 <- svyglm(cf47 ~ brthwk.p.i, design = rchis05, family = quasibinomial)
model3 <- svyglm(referred ~ brthwk.p.i, design = rchis05, family = quasibinomial)

stargazer(model1, model2, model3, type = "text")

summary(model1)
summary(model2)
summary(model3)

cbind(OddsRatio = exp(model1$coef), exp(confint(model1)))
cbind(OddsRatio = exp(model2$coef), exp(confint(model2)))
cbind(OddsRatio = exp(model3$coef), exp(confint(model3)))
```

### Race
```{r}
model1 <- svyglm(cf46 ~ racehp2p, design = rchis05, family = quasibinomial)
model2 <- svyglm(cf47 ~ racehp2p, design = rchis05, family = quasibinomial)
model3 <- svyglm(referred ~ racehp2p, design = rchis05, family = quasibinomial)

stargazer(model1, model2, model3, type = "text")

summary(model1)
summary(model2)
summary(model3)

cbind(OddsRatio = exp(model1$coef), exp(confint(model1)))
cbind(OddsRatio = exp(model2$coef), exp(confint(model2)))
cbind(OddsRatio = exp(model3$coef), exp(confint(model3)))
```

### Hispanic Ethnicity
```{r}
model1 <- svyglm(cf46 ~ srh.a.i, design = rchis05, family = quasibinomial)
model2 <- svyglm(cf47 ~ srh.a.i, design = rchis05, family = quasibinomial)
model3 <- svyglm(referred ~ srh.a.i, design = rchis05, family = quasibinomial)

stargazer(model1, model2, model3, type = "text")

summary(model1)
summary(model2)
summary(model3)

cbind(OddsRatio = exp(model1$coef), exp(confint(model1)))
cbind(OddsRatio = exp(model2$coef), exp(confint(model2)))
cbind(OddsRatio = exp(model3$coef), exp(confint(model3)))
```

### Below Poverty Level
```{r}
model1 <- svyglm(cf46 ~ belowpovl, design = rchis05, family = quasibinomial)
model2 <- svyglm(cf47 ~ belowpovl, design = rchis05, family = quasibinomial)
model3 <- svyglm(referred ~ belowpovl, design = rchis05, family = quasibinomial)

stargazer(model1, model2, model3, type = "text")

summary(model1)
summary(model2)
summary(model3)

cbind(OddsRatio = exp(model1$coef), exp(confint(model1)))
cbind(OddsRatio = exp(model2$coef), exp(confint(model2)))
cbind(OddsRatio = exp(model3$coef), exp(confint(model3)))
```

### Uninsured Ever in Last Year
```{r}
model1 <- svyglm(cf46 ~ unins.ever, design = rchis05, family = quasibinomial)
model2 <- svyglm(cf47 ~ unins.ever, design = rchis05, family = quasibinomial)
model3 <- svyglm(referred ~ unins.ever, design = rchis05, family = quasibinomial)

stargazer(model1, model2, model3, type = "text")

summary(model1)
summary(model2)
summary(model3)

cbind(OddsRatio = exp(model1$coef), exp(confint(model1)))
cbind(OddsRatio = exp(model2$coef), exp(confint(model2)))
cbind(OddsRatio = exp(model3$coef), exp(confint(model3)))
```

### PEDS High Risk
```{r}
model1 <- svyglm(cf46 ~ pedsHiRisk, design = rchis05, family = quasibinomial)
model2 <- svyglm(cf47 ~ pedsHiRisk, design = rchis05, family = quasibinomial)
model3 <- svyglm(referred ~ pedsHiRisk, design = rchis05, family = quasibinomial)

stargazer(model1, model2, model3, type = "text")

summary(model1)
summary(model2)
summary(model3)

cbind(OddsRatio = exp(model1$coef), exp(confint(model1)))
cbind(OddsRatio = exp(model2$coef), exp(confint(model2)))
cbind(OddsRatio = exp(model3$coef), exp(confint(model3)))
```



